FoRTE baseline

### 2019-04-29 analysis/paper/paper.Rmd
[paper] Add takeaways for within vs. across figure

Take-away: Overall, structural uncertainty (variance in ensemble means across structures) is comparable or lower than parameter uncertainty (uncertainty within ensembles for a given structure).

>>>>

Take-away: Overall, structural uncertainty (variance in ensemble means across structures) is comparable or lower than parameter uncertainty (uncertainty within ensembles for a given structure).
Parameter uncertainty varies significantly across model structures.
Enabling trait plasticity increases variance in predictions of AGB.
Enabling the finite canopy radius increases the variance in LAI predictions.
GPP and NPP have the highest variance by far for the combination of finite canopy radius and two-stream radiative transfer.
